A Survey of Physical Design Techniques of Information Systems

### 2010-07-03 trunk/cs848-db/Paper.tex

\usepackage[pdftex]{graphicx}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A Survey of Physical Design Techniques of Information Systems }

@@

Of course, there are other indexing techniques used such as hash tables, and bitmap indices. Bitmap indices are used in Data Warehouses, and will be discussed in details in Section~\ref{SEC-WAREHOUSES}.

@@

\subsection{Clustering}

>>>>

\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{graphicx}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A Survey of Physical Design Techniques of Information Systems}

@@

Of course, there are other indexing techniques used such as hash tables, and bitmap indices. For example, Bitmap indices are commonly used in Data Warehouses, and will be discussed in details in Section~\ref{SEC-WAREHOUSES}.

@@

\subsection{Clustering}
When only records satisfying certain criteria are need from a table, it is often unnecessary to scan the whole table. For example, if only records that occrurred in January 2010 are needed, then querying all the table would be an extremely unnecessary overhead. This is where clustering comes in. Clustering relfects how the records are physically located together on disk. Records that are likely to be queried together will be stored physically together to avoid querying the whole table. For the previously mentioned example, the data can be clustered by month, such that all the records of January 2010 are physically in the same page, for example. In this case, only this page will need to be read. As people realized the potential of clustering, multidimensional clustering was introduced where data is clustered based on different criteria at the same time.
